My title

### 2023-01-26 outputs/paper/paper.qmd
paper created
Plotting data

```{r setup, include = FALSE}
#### Workspace Setup ####
library(haven)
library(tidyverse)
library(knitr)
library(lubridate)
```

@@

```{r}
#### Explore ####
setwd("/cloud/project/inputs/data")
toronto_mci <- readr::read_csv("cleaned_data.csv", show_col_types = FALSE)

#table(toronto_mci$mci_category)

toronto_mci <-
  toronto_mci %>% 
    group_by(month = lubridate::floor_date(occurrencedate, "month")) %>% 
    summarize("Assaults" = sum(mci_category == "Assault"))

@@

toronto_mci

data %>% 
    group_by(month = lubridate::floor_date(date, "month")) %>%
    summarize(summary_variable = sum(value))

unique(toronto_mci$occurrenceyear)

?year()
```

@@

>>>>

```{r setup, include = FALSE}
#### Workspace Setup ####
install.packages("tinytex")
tinytex::install_tinytex()

Ylibrary(tinytex)
library(haven)
library(here)
library(tidyverse)
library(knitr)
library(lubridate)
```

@@

```{r, echo=FALSE}
#### Explore ####
toronto_mci <- 
  read_csv(here::here("inputs/data/cleaned_data.csv"), show_col_types = FALSE)

#names(toronto_mci)
#unique(toronto_mci$mci_category)
toronto_mci <- toronto_mci[order(toronto_mci$occurrencedate),]

#head(toronto_mci)
#tail(toronto_mci)

split_data <- split(toronto_mci, f = toronto_mci$occurrenceyear)

mci_2018 <- split_data$'2018'
mci_2019 <- split_data$'2019'
mci_2020 <- split_data$'2020'
mci_2021 <- split_data$'2021'

toronto_mci2 <-
  toronto_mci %>% 
    group_by(Date = lubridate::floor_date(occurrencedate, "month")) %>% 
    summarize("Assaults" = sum(mci_category == "Assault"), 
              "Robbery" = sum(mci_category == "Robbery"),
              "B_and_E" = sum(mci_category == "Break and Enter"),
              "Auto_Theft" = sum(mci_category == "Auto Theft"),
              "Theft_Over" = sum(mci_category == "Theft Over"))

toronto_mci2 %>% 
  ggplot(aes(x = Date)) + 
  geom_line(aes(y = Assaults), color = "red") +
  geom_line(aes(y = Robbery), color = "blue") +
  geom_line(aes(y = B_and_E), color = "green") +
  geom_line(aes(y = Auto_Theft), color = "orange") +
  geom_line(aes(y = Theft_Over), color = "purple") +
  labs(y = "Occurences")

@@

toronto_mci2
```

@@

```{r, R.options=}
